The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types

### 2023-05-27 final/paper/main.tex
update paper

\title{The Accuracy of KNN, SVM, neural network, naive Bayes classifier and DBSCAN, kmeans for Determining the Cancer by Gene-expression signatures And the Arrhythmia Types}

@@

\bf{support vector machine (SVM)}: \rm{Given} a set of training datas, where each data is labeled as a 
binary class, such as $0$ and $1$, SVM training algorithm creates a model that assigns new examples to 
the binay labels by making it a non-probabilistic binary linear classifier. In addition, accroding to 
\cite{amari1999improving} \cite{hofmann2006support}, SVM can also use a method called kernel trick to 
effectively perform non-linear classification by implicitly mapping its inputs into a high-dimensional 
feature space.

@@

\section{Main Process}
  The main algorithm to process the dataset is shown as below:
  \begin{algorithm}
    \caption{The Main Algorithm}\label{alg:main}
    \begin{algorithmic}[1]
      \Require $\text{Dataset}$
      \State $\text{Data}, \text{Labels} \gets \text{Dataset}$
      \State $\text{Data}' \gets \text{preprocess}(\text{Data})$
      \State $\text{Konwns}, \text{Unkonwns} \gets \text{classify}(\text{Data}')$
      \State $\text{Clusters} \gets \text{clustering}(\text{Unkonwns})$
      \State $\text{Accuracy} \gets \text{calacc}((\text{Konwns}, \text{Clusters}), \text{Labels})$
    \end{algorithmic}
  \end{algorithm}

@@

  From the result, the fact that SVM performs worse than KNN can be seen. The main reason is because the multiple 
  classification SVMs method designed here can't separate well in most of types. Fig~\ref{fig:SVM_fail} illurates the 
  situation. For type 1 SVM, the negative/positive classification makes the data hard to separate, and also for type 
  2, 3, etc. This happens even when the kernel trick is applied, though the kernel trick sometimes ease the pain. 
  \begin{figure}[htb]
    \centering
    \includegraphics[scale=0.15]{assets/SVM_fail.pdf}
    \caption{An example that multiple SVMs fail}
    \label{fig:SVM_fail}
  \end{figure}

@@

\section{Conclusion}

>>>>

\title{The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types}

@@

\bf{support vector machine (SVM)}: \rm{Given} a set of training datas, where each data is labeled as a 
binary class, such as $0$ and $1$, SVM training algorithm creates a model that assigns new examples to 
the binay labels by making it a non-probabilistic binary linear classifier. In addition, accroding to 
\cite{amari1999improving} \cite{hofmann2006support}, SVM can also use a method called kernel trick to 
effectively perform non-linear classification by implicitly mapping its inputs into a high-dimensional 
feature space. 
The idea of kernel trick is transform the data into higher dimension. In ideal situation, the dataset 
which is not linear separable becomes linear separable. Fig~\ref{fig:SVM_kernel_trick} illurates this 
case.

\begin{figure}[htb]
    \centering
    \includegraphics[scale=0.25]{assets/SVM_kernel_trick.png}
    \caption{An example of SVM kernel trick}
    \label{fig:SVM_kernel_trick}
\end{figure}

@@

\section{Main Process}
  The pesudo code of the proposed algorithm to process the dataset is shown below and Fig~\ref{fig:Main_Algo} 
  illurates the process of this algorithm:
  \begin{algorithm}
    \caption{The Main Algorithm}\label{alg:main}
    \begin{algorithmic}[1]
      \Require $\text{Dataset}$
      \State $\text{Data}, \text{Labels} \gets \text{Dataset}$
      \State $\text{Data}' \gets \text{preprocess}(\text{Data})$
      \State $\text{Konwns}, \text{Unkonwns} \gets \text{classify}(\text{Data}')$
      \State $\text{Clusters} \gets \text{clustering}(\text{Unkonwns})$
      \State $\text{Accuracy} \gets \text{calacc}((\text{Konwns}, \text{Clusters}), \text{Labels})$
    \end{algorithmic}
  \end{algorithm}

  \begin{figure}[htb]
    \centering
    \includegraphics[scale=0.20]{assets/Main_Algo.pdf}
    \caption{A figure about the main algorithm}
    \label{fig:Main_Algo}
  \end{figure}

@@

  From the result, the fact that SVM performs worse than KNN can be seen. The main reason is because the mult- 
  classification SVMs method designed here can't separate well in most of types. Fig~\ref{fig:SVM_fail} illurates the 
  situation. For type 1 SVM, the negative/positive classification makes the data hard to separate, and also for type 
  2, 3, etc. This happens even when the kernel trick is applied, though the kernel trick sometimes ease the pain. 
  \begin{figure}[htb]
    \centering
    \includegraphics[scale=0.15]{assets/SVM_fail.pdf}
    \caption{An example that mult-classification SVMs fail}
    \label{fig:SVM_fail}
  \end{figure}

@@

\section{Conclusion}
In this study, we present a framework of algorithm to deal with the dataset containing 
out-of-knowledge data. And with in this algorithm, multiple major machine learning 
techniques are used, e.g., for preprocess, PCA, AE, normalization; for classification, 
KNN, SVM, SVDD, NN, as for clustering, DBSCAN, k-means, NN-chain. Among the various 
combinations, PCA + KNN + k-means performs outstanding in gene expression cancer RNA-Seq 
dataset, and raw data + KNN + k-means performs the best in arrhythmia dataset. Accidently, 
SVM performs bad in these two dataset. The main cause is the defect of the multi-classification 
SVMs design, which make some SVMs hard to separate the target types. However, by customize 
the kernel for each SVMs, the problem may ease. In the same time, the increasing number of 
parameters can be fine-tuned by metaheuristic algorithms, e.g., simulated annealing, genetic 
algorithm, etc. We will develope a refinement design on multi-classification SVMs, to enhance 
the accuracy on these datasets.

\section{Contribution}
\begin{itemize}
  \item Hsieh Cheng-Han: KNN, SVM, DBSCAN, paper, ppt
  \item Hsu Ting-Hao: 
  \item Sun Shih-Yu: SVM, k-means, paper
  \item Lu Che-Yuan: 
  \item Huang Chia-Yen: 
\end{itemize}
